\subsection{Android}
The Android component of the system was implemented with the Android 4's design principles in mind. 
This means that the ActionBar has taken over the role traditionally occupied by the menu in previous versions of Android. 
Furthermore, emphasis has shifted away from Activity-centric to Fragment-oriented applications which allows for faster,
 more dynamic and interactive applications. With this in mind it was decided to
 implement the main section of our application as a single activity, called
 HomeActivity, which hosts different tabs for each main view (Product Scanner,
 Product Browser and Shopping List Browser) of our application.
 Each view would then be implemented as a series of Fragments which would move in and out of
 their respective tabs depending on the state of the view. The other views in
 our application (Graph View and Directions View) will be implemented as
 seperate activities which can be launched from our HomeActivity. Unfortunately
 much of this required functionality is not compatible with Android versions
 older than Honeycomb, therefore we needed a workaround. Fortunately this was
 available in the form of the ActionBar Sherlock and android support, libraries
 which provide us with Android 4 functionality on older versions of Android.  \\
 Our application, as mentioned previously mentioned, makes use of HTTP requests
 and JSON to send and receive data with the server's datastore. However it would
 be quite data intensive to require the application to request data everytime a
 search is done. It was therefore decided to make use of a local database to
 store the data as well, with the user being able to define how often to update
 this data. Only the initial loading of data, updating of product prices and
 usage of the Directions Viewer therefore explicitly require an active data
 connection. Sqlite was chosen as the local database management system due to it
 being integrated into the Android OS and having good support within the Android
 SDK. db4o was considered at first since it would allow us to easily store and
 retrieve entire objects, but it proved to be too slow and resource hungry.
\input{and-ps-impl}
\input{and-pb-impl}
\input{and-sl-impl}
\input{and-gv-impl}
\input{and-dv-impl}
