\section{Evaluation}
The project has resulted in a working prototype of a pricetracking system. It is
fairly usable at the moment but there are a few problems with it that would need
to be addressed in order to take the system to the market. Firstly we need to
obtain more data. One could say we simply need to get more users downloading our
app, however this is not viable due to it being of minimal use to them if there
is no data for their area. A solution to this dilema would be to build a
webcrawler which would scour store websites every week for product prices and
thereby provide us with a large amount of data on a weekly basis even though we
do not have a lot of users. Secondly another method of obtaining product data
via users must be looked into since typing in product information can be a
laborius task for some. We should therefore investigate OCR as a method of
scanning in either shopping slip or product labels. This would prevent users
from having to type product information themselves and would instead allow them
to simply scan and view the product. Thirdly, the server would need to be
upgraded since it only has 9 hours of up time per day which means that it needs
to be periodically switched off in order to be available throughout the day.
Lastly, we could look to include a social aspect to the system. This could be
done by allowing users to sign in with a variety of social networks and
``reward'' users in some way when they scan products. This would also allow the
application to gain more publicity.
