\subsection{GAE}
In order to understand how the system will function it is important to get an idea of how and what data will be stored.
Our entities within the Datastore are the following:
\begin{description}
\item [ProductCategory] Three nested categories associated with a product, e.g. Coffee Beans, Coffee, Consumables.
\item [Brand] Brand associated with a product, e.g. Jacobs.
\item[Product] A specific product, e.g. 500g Frisco.
\item[Country] A country, e.g. South Africa.
\item[Province] A province or state, e.g. Western Cape.
\item [City] A city or town, e.g. Stellenbosch.
\item [CityLocation] A GPS location together with its closest city.
\item [Store] A store franchise, e.g. Spar.
\item [Branch] A branch of a Store, e.g. Eikestad Woolworths.
\item [BranchProduct] The entity associated with a product at a specific branch.
\item [DatePrice] The price associated with a BranchProduct on a particular Date.
\end{description}
A clearer picture of the system is given in Figure 12.
\input{entity-diag}
The entities all have their own Data Access Objects (DAOs) which allow for querying, 
get and put operations. The DAOs are static objects which provide a simple interface for interacting with the
Objectify-AppEngine Datastore. They are all created when the system is loaded.
Each of the services used by the GWT front-end has an implementation on the GAE back-end. These are:
\begin{description}
\item[ClassService] Registers entities with Objectify. Also fetches a
particular class of entities, deletes or updates an entity for Admin Viewer.
\item[BranchProductService] Retrieves the following:
\begin{itemize}
\item BranchProducts which match a ProductCategory and/or a City or a Product.
\item Branches which stock a set of Products.
\item BranchProducts's price histories.
\end{itemize}
\item[ProductService] Retrieves all Products from the Datastore.
\item[CategoryService] Retrieves all Categories from the Datastore.
\item[LocationService] Retrieves all cities, countries or provinces from the
Datastore.
\end{description}
