\subsection{GWT}
The GWT front-end has several central components which facilitate interaction between the subsystems described in Design.
In the *.client package we have:
\begin{description}
\item[WebSystem] The central system which:\begin{itemize}
\item Controls how the system interacts with GAE,
\item Requests data for and loads data into the Graphical User Interface (GUI),
\item Serves as the entry point for the system, and
\item Binds the different components together.
\end{itemize}  
\item[RPC] Responsible for interacting with the Datastore via RPCs. It provides the following services:  
\begin{itemize}
\item ClassService
\item BranchProductService
\item ProductService
\item ProductCategoryService
\item LocationService
\item GeoService : Determines user location using a GWT implementation of HTML5's GeoLocation~\cite{geo} interface.
\end{itemize}
 \item[SystemData] Stores data pulled from the Datastore.
\end{description}
 In the *.client.gui.* package we have:
 \begin{description}
  \item[WebPage] Holds the various GUI components. Facilitates interaction between GUI components.
  \item[ViewTree] Provides sidebar with shortcuts to each of the major components. 
  \item[button.*] Contains custom image buttons.
    \item[loader.Loader] A loader to be displayed when the system is busy.
    \item[popup.FocusedPopupPanel] A general purpose PopupPanel which disables the background when shown.
    \item[spinedit.SpinEdit] A SpinEdit (up and down button with an IntegerBox).
    \item[table.TableView] A general purpose table display created using a FlexTable.
\end{description}
 In the *.client.util package we have:
 \begin{description}
  \item[CSSUtils] Used to inject custom css styles.
  \item[GUIUtils] Provides static access to error dialogs and the loader.
    \item[ImageUtils] Provides easy access to images.
    \item[Utils] Provides some general methods needed by some of the GUI components.
\end{description}
\input{gwt-pb-impl}
\input{gwt-sl-impl}
\input{gwt-av-impl}
\input{gwt-gv-impl}
\input{gwt-dv-impl}
