\section{Current Solutions}

There are a number of mobile applications available which are used to improve users's shopping experience. Many of these use bar code scanning to fetch product information, however most of them don't work in South Africa. Some of the current solutions are:
\begin{description}
\item[Google Shopper~\cite{google}] Google's take on a shopping assistant. This app provides:
\begin{itemize}
\item Bar code scanning of products to obtain information about them.
\item Scanning of a CD, DVD, book or video game's cover art to obtain information about it.
\item Voice search for products.
\item Price comparison
\item View nearby offers via Google Places.
\item Save your history, create favourites.
\item Share deals using social media.
\item View nearby stores and directions.
\item Not currently available in South Africa.
\item No web implementation.
\end{itemize}
\item[Barcode Scanner~\cite{scanner}] A very popular bar code scanner. It :
\begin{itemize}
\item Uses open source bar code processing Java library (ZXing).
\item Uses Google Product Search and Google Web Search to find information about bar codes.
\item No web implementation.
\end{itemize}
\item[ShopSavvy~\cite{shopsavvy}] The leader in mobile shopping provides the following :
\begin{itemize}
\item Uses bar code scanning and normal searching.
\item Allows users to make purchases from within app.
\item Allows users to create new products for unidentified items.
\item Provides information about deals, e.g. coupons and weekend sales.
\item No web implementation.
\item Not currently available in South Africa.
\end{itemize}
\item[PriceCheck~\cite{pricecheck}] A South African price comparison site and app. It provides the following:
\begin{itemize}
\item Price comparison.
\item Uses bar code scanning, normal searching and browsing.
\item Online searching, browsing and shopping as well.
\item Only recently started integrating grocery shopping.
\item Around since 2006, owned by Naspers.
\item Provides user registration and favourites.
\item Product and retailer rereviews.
\item Available on Android, iOS and Blackberry.
\end{itemize}
\end{description}
It is clear that although there are currently solutions which approach our problem, most of them quite match up to what we want to do, mostly due to lacking support in South Africa or lacking web support. PriceCheck is the only current solution that can be considered a direct competitor and it has only recently branched into grocery shopping with most of its focus lying elsewhere.
